$Z_3$ topological order in the quantum dimer-pentamer model

### 2016-05-14 qdpm_paper.tex
Figures

@@

 %%%%%%%%%%%%%%%%%
\begin{figure}[tpb]
\centering
\includegraphics[width=0.8\linewidth]{pentamer_moves.pdf}
\caption{a) Horizontal creation an annihilation, b) horizontal move \textcolor{red}{Owen:fix this move}, c) diagonal moves \textcolor{red}{Owen: Remove (d) as it is related to (c) by rotational symmetry}}
\label{fig:pentamer_moves}
\end{figure}
%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%
    \begin{figure}
        \centering
        \includegraphics[width=0.75\columnwidth]{dimer_gry_scale_qdpm.pdf}
        \caption{Gray scale of the dimer correlation function between the dimer in the upper
        left corner (colored red) and all other dimers on a $16\times16$ lattice. The 
         red dimers indicate correlations that are off the scale shown at the
        bottom of the figure. \textcolor{red}{Owen: make the origin dimer a different color that the off-scale dimers}.}
        \label{fig:dimer_gry_scale_qdpm}
    \end{figure}
%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
    \centering
    \includegraphics[width=1.0\columnwidth]{spacial_dmr_cor.pdf}
    \caption{Correlation function between parallel dimers one the same (blue) and different (red) 
    sub-lattice on an $L=32$ lattice. The lines represent least-squares fits to exponential decay. }
    \label{fig:spatial_dmr_cor}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%
   \begin{figure}[]
        \centering
        \includegraphics[width=0.75\columnwidth]{qdpm_dmr_vis_HM_16x16.pdf}
        \caption{QDPM dimer structure factor $\gamma=0.5$.}
        \label{fig:spacial_dmr_z3vis_cor}
    \end{figure}
%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%
    \begin{figure}[]
        \centering
        \includegraphics[width=1.0\columnwidth]{vis_dmr_qdpm_struc_fac_16x16.pdf}
        \caption{The QDPM dimer structure factor $S_d(k)$ and $Z_3$ vison structure factor $S_v(k)$
        shown along the path in $k$ space connecting the $(0,0)$, to $(\pi,0)$, $(\pi,\pi)$, $(0,0)$
        points for $\gamma=0.5$.}
        \label{fig:vis_dmr_cut}
    \end{figure}
%%%%%%%%%%%%%%%%%%%%%%%

>>>>

\newcommand*{\pentmvcreate}{%
    ]{Symbols/pentmvcreate1.pdf} }
\newcommand*{\pentmvanal}{%
    ]{Symbols/pentmvcreate2.pdf} }

@@

 %%%%%%%%%%%%%%%%%
%\begin{figure}[tpb]
%\centering
%\includegraphics[width=0.8\linewidth]{pentamer_moves.pdf}
%\caption{a) Horizontal creation an annihilation, b) horizontal move \textcolor{red}{Owen:fix this move}, c) diagonal moves \textcolor{red}{Owen: Remove (d) as it is related to (c) by rotational symmetry}}
%\label{fig:pentamer_moves}
%\end{figure}
%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}
  \begin{tabular}{| l | c | }
  	\hline
    $c1$, $\bar{c}1$ & $\pentmvcreate$, $\pentmvanal$ \\
	\hline
  \end{tabular}
  \caption{Defects where $n_v$ dimers touch a vertex and their associated $U(1)$ charges on the A sub-lattice in both the QDM and QFPLM. Defects on the B sub-lattice have opposite charge.}
  \label{tab:defects}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%
    \begin{figure}
        \centering
        \includegraphics[width=0.5\columnwidth]{dimer_gry_scale_qdpm.pdf}
        \caption{Gray scale of the dimer correlation function between the dimer in the upper
        left corner (colored red) and all other dimers on a $16\times16$ lattice. The 
         red dimers indicate correlations that are off the scale shown at the
        bottom of the figure. \textcolor{red}{Owen: make the origin dimer a different color that the off-scale dimers}.}
        \label{fig:dimer_gry_scale_qdpm}
    \end{figure}
%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
    \centering
    \includegraphics[width=1.0\columnwidth]{spacial_dmr_cor.pdf}
    \caption{Correlation function between parallel dimers one the same (blue) and different (red) 
    sub-lattice on an $L=32$ lattice. The lines represent least-squares fits to exponential decay. }
    \label{fig:spatial_dmr_cor}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%
   \begin{figure}[]
        \centering
        \includegraphics[width=1.0\columnwidth]{qdpm_dmr_vis_HM_16x16.pdf}
        \caption{QDPM dimer structure factor $\gamma=0.5$.}
        \label{fig:spacial_dmr_z3vis_cor}
    \end{figure}
%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%
    \begin{figure}[]
        \centering
        \includegraphics[width=1.0\columnwidth]{vis_dmr_qdpm_struc_fac_16x16.pdf}
        \caption{The QDPM dimer structure factor $S_d(k)$ and $Z_3$ vison structure factor $S_v(k)$
        shown along the path in $k$ space connecting the $(0,0)$, to $(\pi,0)$, $(\pi,\pi)$, $(0,0)$
        points for $\gamma=0.5$.}
        \label{fig:vis_dmr_cut}
    \end{figure}
%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%
    \begin{figure}[]
        \centering
        \includegraphics[width=1.0\columnwidth]{monomer_cor_log.pdf}
        \caption{Monomer correlations in the QDPM.}
        \label{fig:vis_dmr_cut}
    \end{figure}
%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%
